### 2021-05-04 content/80.formal-definition.tex
Cite RFC and use `backticks` font

    𝕃ro-crate = { Property(p), Class(c), Literal(x), ℝ, 𝕊 }
    𝔻 =  𝕀𝕣𝕚
    𝕀𝕣𝕚 ≡  { IRIs as defined in <https://tools.ietf.org/html/rfc3987> }
    ℝ ≡  { real or integer numbers }
    𝕊 ≡  { literal strings }

The domain of discourse is the set of 𝕀𝕣𝕚 identifiers (notation `<http://example.com/>`), with additional descriptions using numbers ℝ (notation `13.37`) and literal strings 𝕊 (notation `“Hello”`).

From this formalized language `𝕃ro-crate` a RO-Crate can be interpreted in any representation that can gather these descriptions, their properties, classes, and literal attributes.

@@

The `Root(r)` is a type of Dataset(r), and must have the metadata to literal attributes to provide a `name`, `description` and `datePublished`, as well as a contextual entity identifying its license. These predicates correspond to the RO-Crate 1.1 [requirements for the root data entity](https://www.researchobject.org/ro-crate/1.1/root-data-entity.html#direct-properties-of-the-root-data-entity).

>>>>

    𝕃ro-crate = { Property(p), Class(c), Literal(x), ℝ, 𝕊 }
    𝔻 =  𝕀𝕣𝕚
    𝕀𝕣𝕚 ≡  { IRIs as defined in RFC3987 }
    ℝ ≡  { real or integer numbers }
    𝕊 ≡  { literal strings }

The domain of discourse is the set of `𝕀𝕣𝕚` identifiers [@doi:10.17487/rfc3987] (notation `<http://example.com/>`), with additional descriptions using numbers ℝ (notation `13.37`) and literal strings `𝕊` (notation `“Hello”`).

From this formalized language `𝕃ro-crate` an RO-Crate can be interpreted in any representation that can gather these descriptions, their properties, classes, and literal attributes.

@@

The `Root(r)` is a type of `Dataset(r)`, and must have the metadata to literal attributes to provide a `name`, `description` and `datePublished`, as well as a contextual entity identifying its license. These predicates correspond to the RO-Crate 1.1 [requirements for the root data entity](https://www.researchobject.org/ro-crate/1.1/root-data-entity.html#direct-properties-of-the-root-data-entity).
